---
title: "Duke Faculty Sampling Frame and 20% Stratified Sample"
output: html_document
params:
  run_frame_scrape: false
---

This document constructs the faculty sampling frame before collecting any
professor-level outcomes. It keeps every appointment category returned by the
Scholars `Faculty` filter, excludes the four agreed departments or institutes,
assigns each person to one mutually exclusive sampling department, and selects
approximately 20% within every department.

The search page is rendered with JavaScript, so the frame collector uses a
headless Chrome session through `chromote`. Set `run_frame_scrape: true` in the
YAML header when you are ready to collect the frame.

```{r setup, message=FALSE, warning=FALSE}
required_packages <- c(
  "dplyr", "jsonlite", "purrr", "readr", "stringr", "tibble", "tidyr"
)
if (params$run_frame_scrape) required_packages <- c("chromote", required_packages)

missing_packages <- setdiff(required_packages, rownames(installed.packages()))
if (length(missing_packages) > 0) {
  stop(
    "Install these packages before running the document: ",
    paste(missing_packages, collapse = ", ")
  )
}

library(dplyr)
library(jsonlite)
library(purrr)
library(readr)
library(stringr)
library(tibble)
library(tidyr)

if (params$run_frame_scrape) library(chromote)

source("R/config.R")

dir.create("data/raw", recursive = TRUE, showWarnings = FALSE)
dir.create("cache/frame", recursive = TRUE, showWarnings = FALSE)
```

## Fixed design rules

- Include all appointment categories returned by the Scholars `Faculty` filter.
- Include only the 17 departments in `included_departments`.
- Exclude Duke Science & Society, Duke Institute for Brain Sciences, Sanford,
  and Electrical and Computer Engineering.
- Keep one row per unique Scholars profile.
- For a person returned by multiple included department searches, retain every
  affiliation in `departments` and assign the alphabetically first department
  as `sampling_department`. This deterministic rule is applied before outcomes
  are collected.
- Select approximately 20% without replacement inside each sampling department.
- Never replace a selected profile because its outcome information is missing.

## Browser helpers

```{r helpers}
encode_query_value <- function(x) {
  utils::URLencode(x, reserved = TRUE)
}

department_search_url <- function(department, page = 1L) {
  paste0(
    search_base_url,
    "?q=%2A&tab=people&pplptf%5B%5D=Faculty",
    "&suf%5B%5D=", encode_query_value(school_unit),
    "&df%5B%5D=", encode_query_value(department),
    "&ppls=Person+a-z&pplsp=", page
  )
}

evaluate_value <- function(browser, expression) {
  browser$Runtime$evaluate(
    expression = expression,
    returnByValue = TRUE,
    awaitPromise = TRUE
  )$result$value
}

wait_for_people <- function(browser, timeout_seconds = 30) {
  started <- Sys.time()
  repeat {
    count <- evaluate_value(
      browser,
      "document.querySelectorAll('#people a[href*=\"/person/\"]').length"
    )
    if (!is.null(count) && count > 0) return(invisible(TRUE))
    if (difftime(Sys.time(), started, units = "secs") > timeout_seconds) {
      stop("Timed out waiting for faculty results.")
    }
    Sys.sleep(0.25)
  }
}

read_result_page <- function(browser, department, page) {
  url <- department_search_url(department, page)
  browser$Page$navigate(url)
  wait_for_people(browser)

  json <- evaluate_value(
    browser,
    paste0(
      "JSON.stringify(Array.from(",
      "document.querySelectorAll('#people a[href*=\"/person/\"]')",
      ").map(a => ({",
      "profile_url: new URL(a.getAttribute('href'), location.origin).href,",
      "link_text: (a.textContent || '').trim()",
      "})))"
    )
  )

  fromJSON(json) |>
    as_tibble() |>
    filter(str_detect(profile_url, "^https://scholars\\.duke\\.edu/person/")) |>
    mutate(
      faculty_id = str_remove(profile_url, ".*/person/"),
      department = department,
      page = page
    ) |>
    filter(nzchar(link_text)) |>
    group_by(faculty_id, profile_url, department, page) |>
    # A profile may have several links. The shortest nonempty label is normally
    # the displayed name rather than the full result-card description.
    summarise(name = link_text[which.min(nchar(link_text))], .groups = "drop")
}

read_department_frame <- function(browser, department) {
  browser$Page$navigate(department_search_url(department, 1L))
  wait_for_people(browser)

  total_text <- evaluate_value(
    browser,
    "document.querySelector('#people')?.innerText.match(/Showing 1\\s*-\\s*20 of [0-9,]+/)?.[0] || ''"
  )
  total <- parse_number(str_extract(total_text, "[0-9,]+$"))
  if (is.na(total)) stop("Could not determine result count for ", department)

  pages <- seq_len(ceiling(total / 20))
  message(department, ": ", total, " results across ", length(pages), " pages")

  map_dfr(pages, function(page) {
    if (page > 1L) Sys.sleep(0.75)
    read_result_page(browser, department, page)
  }) |>
    distinct(faculty_id, department, .keep_all = TRUE)
}
```

## Build the frame

```{r build-frame, eval=params$run_frame_scrape}
browser <- ChromoteSession$new()
on.exit(browser$close(), add = TRUE)

department_memberships <- map_dfr(
  included_departments,
  ~ read_department_frame(browser, .x)
)

write_csv(
  department_memberships,
  "data/raw/faculty_department_memberships.csv"
)

faculty_frame <- department_memberships |>
  arrange(faculty_id, department) |>
  group_by(faculty_id, profile_url) |>
  summarise(
    name = name[which.min(nchar(name))],
    departments = paste(sort(unique(department)), collapse = " | "),
    department_count = n_distinct(department),
    sampling_department = sort(unique(department))[1],
    .groups = "drop"
  ) |>
  arrange(sampling_department, name, faculty_id)

stopifnot(!anyDuplicated(faculty_frame$faculty_id))
stopifnot(all(faculty_frame$sampling_department %in% included_departments))
stopifnot(!any(map_lgl(
  faculty_frame$departments,
  ~ any(str_detect(.x, fixed(excluded_departments)))
)))

write_csv(faculty_frame, "data/raw/faculty_sampling_frame.csv")

faculty_frame |>
  count(sampling_department, name = "N_h")
```

## Draw the 20% stratified sample

```{r draw-sample, eval=params$run_frame_scrape}
allocation <- faculty_frame |>
  count(sampling_department, name = "N_h") |>
  mutate(
    quota = sampling_fraction * N_h,
    n_h = floor(quota),
    remainder = quota - n_h
  ) |>
  arrange(desc(remainder), sampling_department)

target_n <- round(sampling_fraction * nrow(faculty_frame))
remaining <- target_n - sum(allocation$n_h)

allocation <- allocation |>
  mutate(n_h = n_h + as.integer(row_number() <= remaining)) |>
  arrange(sampling_department)

set.seed(random_seed)
sampled_faculty <- faculty_frame |>
  left_join(allocation, by = "sampling_department") |>
  group_by(sampling_department) |>
  group_modify(~ slice_sample(.x, n = first(.x$n_h))) |>
  ungroup() |>
  mutate(
    selection_probability = n_h / N_h,
    survey_weight = 1 / selection_probability,
    random_seed = random_seed
  ) |>
  arrange(sampling_department, name)

stopifnot(nrow(sampled_faculty) == target_n)
stopifnot(!anyDuplicated(sampled_faculty$faculty_id))

write_csv(allocation, "data/raw/sample_allocation.csv")
write_csv(sampled_faculty, "data/raw/sampled_faculty.csv")

allocation
```

## Frame checks

```{r checks, eval=params$run_frame_scrape}
tibble(
  check = c(
    "Unique faculty in frame",
    "Target sample size",
    "Actual sample size",
    "Faculty with multiple included departments",
    "Duplicate faculty IDs in sample"
  ),
  value = c(
    nrow(faculty_frame),
    target_n,
    nrow(sampled_faculty),
    sum(faculty_frame$department_count > 1),
    anyDuplicated(sampled_faculty$faculty_id)
  )
)
```

The resulting `sampled_faculty.csv` is the only list that should be passed to
the detailed professor-and-grant collector.
